### 2014-02-08 acknowledgements.tex
moved Ned from acknow -> author list
added Duke PAs to acknowledgements
modified format and cover letter for Ultrasonic Imaging submission

\section*{Acknowledgements}
The authors would like to thank Siemens Medical Solution USA, Ultrasound
Division for their in-kind technical support and Ned Danieley for computer
system administration support.  This work was supported by NIH R01CA142824 and
the Duke Coulter Translational Grant Program.

>>>>

\section*{Acknowledgements} 
The authors would like to thank Siemens Medical Solution USA, Ultrasound
Division for their in-kind technical support.  Special thanks to Ned Danieley
for computer system administration support, the pathology assistants and Dr.
John Madden in the Duke University Medical Center for their gross prostate
organ processing, and Matthew Brown for his assistance in designing the optical
prostate rotation feedback system.  This work was supported by NIH R01CA142824
and the Duke Coulter Translational Grant Program.

### 2014-02-08 coverletter.tex
modified format and cover letter for Ultrasonic Imaging submission

\begin{document}
\begin{minipage}[t]{0.5\linewidth}
\vspace{0pt}
\includegraphics[width=3.0in,trim=55 50 50 85,clip=true]{/home/mlp6/bme/Duke_BME_Logos/Pratt-HorizontalLogo-Vector-Black}
\end{minipage}\hfill
\begin{minipage}[t]{0.5\linewidth}
\vspace{0pt}
\hfill{\bf Biomedical Engineering}\\

@@

Re: Ultrasonic Imaging Manuscript Submission
\vspace{0.25in}

@@

We thank you for taking the time and effort to review our manuscript, titled
{\it ``Acoustic Radiation Force Impulse (ARFI) Imaging Prostate Zonal Anatomy:
    Comparison with Endorectal T2-Weighted MR Imaging (T2WI)''}, for
consideration to be published in Ultrasonic Imaging.  All of the authors on
this manuscript have reviewed its content and approve of its submission.  This
work has not been published or submitted for review to any other journals.

@@

%\hspace*{0.575\textwidth} Sincerely,
Sincerely,\\
\includegraphics{/home/mlp6/MarkLPalmeriSig}\\
%\vspace*{0.5in}
Mark L. Palmeri, M.D., Ph.D.\\
\end{Large}
Assistant Research Professor\\
Biomedical Engineering \& Anesthesiology
%\hspace*{0.575\textwidth} Mark L. Palmeri, M.D., Ph.D.\\
%\hspace*{0.575\textwidth} Assistant Research Professor\\
%\hspace*{0.575\textwidth} Biomedical Engineering \& Anesthesiology
\end{document}

>>>>

\newcommand{\journal}{Ultrasonic Imaging}
\begin{document}
\begin{minipage}[t]{0.5\linewidth}
\vspace{0pt}
\includegraphics[width=3.0in,trim=55 50 50 85,clip=true]{/home/mlp6/Documents/Duke_BME_Logos/Pratt-HorizontalLogo-Vector-Black}
\end{minipage}\hfill
\begin{minipage}[t]{0.5\linewidth}
\vspace{0pt}
\hfill{\bf Biomedical Engineering}\\

@@

Re: \journal~Manuscript Submission
\vspace{0.25in}

@@

We thank you for taking the time and effort to review our manuscript, titled
{\it ``Acoustic Radiation Force Impulse (ARFI) Imaging Prostate Zonal Anatomy:
    Comparison with 3T T2-Weighted MR Imaging (T2WI)''}, for consideration to
be published in \journal.

All of the authors on this manuscript have reviewed its content and approve of
its submission.

This work has not been published in or submitted for review to any other
journals.

The human subject data presented in this manuscript was acquired in a Duke
University Medical Center IRB-approved study, with all study subjects providing
written informed consent.

@@

%\hspace*{0.575\textwidth} Sincerely,
Sincerely,\\
\includegraphics{/home/mlp6/Documents/MarkLPalmeriSig}\\
%\vspace*{0.5in}
Mark L. Palmeri, M.D., Ph.D.\\
\end{Large}
Assistant Research Professor\\
Biomedical Engineering \& Anesthesiology
%\hspace*{0.575\textwidth} Mark L. Palmeri, M.D., Ph.D.\\
%\hspace*{0.575\textwidth} Assistant Research Professor\\
%\hspace*{0.575\textwidth} Biomedical Engineering \& Anesthesiology
\end{document}

### 2014-02-08 image_proc_methods.tex
modified format and cover letter for Ultrasonic Imaging submission

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
\subsubsection{MR Image Segmentation and Modeling}
Axial MR T2WI images were manually segmented using the smooth polygon tool in
ITK-SNAP (\url{http://www.itksnap.org})~\cite{Yushkevich2006}, using unique labels for the PZ, CG and AFS. The
gland was segmented from base-to-apex.  The base was identified below the
bladder, and subsequent images were segmented until the last slice with visible
prostatic tissue was identified caudally. The CG, urethra, PZ and AFS were
segmented independently according to their well-established anatomical
characteristics on
T2WI.~\cite{Barentsz2012,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogeneous high signal intensity on T2WI, which is usually
similar to that of the nearby peri-prostatic fat. The CG was visualized and
delineated based on its heterogeneous, lower signal intensity and its location
(Figure~\ref{fig:mr_anatomy}). The urethra was included in the CG segmentation.
When visible, the AFS was identified by its low T2 signal intensity and its
location anterior to the CG.

@@

Segmented image stacks were imported into 3D Slicer (\url{http://www.slicer.org}, v4.3.0)~\cite{Fedorov2012} and 3D
models were rendered using the following parameters (Table~\ref{tab:3dslicer}):

>>>>

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
\subsubsection{MR Image Segmentation and Modeling}
Axial MR T2WI images were manually segmented by an experienced radiologist
using the smooth polygon tool in ITK-SNAP
(http://www.itksnap.org)~\cite{Yushkevich2006}, using unique labels for
the PZ, CG and AFS. The gland was segmented from base-to-apex.  The base was
identified below the bladder, and subsequent images were segmented until the
last slice with visible prostatic tissue was identified caudally. The CG,
urethra, PZ and AFS were segmented independently according to their
well-established anatomical characteristics on
T2WI.~\cite{Barentsz2012,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogeneous high signal intensity on T2WI, which is usually
similar to that of the nearby peri-prostatic fat. The CG was visualized and
delineated based on its heterogeneous, lower signal intensity and its location
(Figure~\ref{fig:mr_anatomy}). The urethra was included in the CG segmentation.
When visible, the AFS was identified by its low T2 signal intensity and its
location anterior to the CG.

@@

Segmented image stacks were imported into 3D Slicer (http://www.slicer.org, v4.3.0)~\cite{Fedorov2012} and 3D
models were rendered using the following parameters (Table~\ref{tab:3dslicer}):
